\acknowledgments
I would never have completed this work without the help from many people. First of all, I thank my advisor, Professor Xun Huang, for his kind mentoring, helpful advices, and encouragement. I have got generous material support, well-condition laboratory experiences and engineering-oriented practice.  

I thank the members of my thesis committee, Professor Xin Zhang for his insightful comments on improving this work. 

I thank my colleagues in HKUST -- Huanxian Bu, Zheng Liu, Wei Feng, Jiafeng Wu, Jingwen Guo, Jiaqi Song and many others. We have finished several deadlines and projects as a team. In daily life, we have been good friends and enjoy many activities in school campus. Without them, my graduate study in HKUST would not be so colorful. 

I give my special thanks to Dr.Pok Wang KWAN who spent nearly a whole year instructing me on how to do research. He gave the project a lot of remarkable ideas using his sufficient engineering background and rich industry experience. When everything goes more and more complicated, his clear mind and intuition always work quite well. I learned how to proceed an engineering research project and how to analyse problems logically and incrementally from his face to face teaching.

I thank Github user Cheedoong and wenbinf for their contribution and sharing of the HKUST Latex thesis Template. This thesis is writing in Latex based on that template-ustthesis Latex class. It saves me a lot of time to do typesetting and let me focus on the contents.   

I thank my parents for their support and encouragement. 

Hope this thesis will not be the end of my academia, I hope the first half sentence is not just a hope.

\endacknowledgments
